---
title: "final project presentation"
author: "Jordan Loflin"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages Used

The only package I used was tidyverse for data manipulation and plotting. This was the only one necessary for my plots.

```{r, echo = TRUE}
library(tidyverse)
```

## Happiness Dataset

The dataset I used was a compiled version of data from the World Happiness Report up to 2022. [World Happiness Report up to 2022](https://www.kaggle.com/datasets/mathurinache/world-happiness-report/224525?select=2019.csv).

The last time this dataset was updated was 2022. The data was not completed and therefore needed to be cut out of the dataset.

**Variables in the dataset:**

-   `Happiness Rank`: Ranking of all the countries in order of happiness
-   `Country`: Representing 149 countries
-   `Region`: 16 represented regions (11 used on my graphs)
-   `Happiness` : Happiness on a scale from 1-10

## 

-   `Economy`: Percentage of how much this affected happiness
-   `Family` :
-   `Life_Exp` :
-   `Freedom`
-   `Trust_Corruption`:
-   `Generosity`:
-   `Year`: From 2015-2021

```{r}
happydata <- read_csv("data/world-happiness-report-2015-2021.csv")
```

## 

```{r}
happydata %>% 
  filter(Year == 2019) %>%
ggplot(aes(x = Happiness)) +
  geom_histogram(bins = 10, color = "plum4", fill = "plum1") + 
  theme() +
  labs( title = "Which regions of the world are the happiest?",
        subtitle = "Data includes 11 different regions in 2019", 
        caption = " The - region represents 10 different countries",
    x = "Happiness") +
  facet_wrap(.~Region, ncol = 4)
```

## 

```{r}
happydata %>% 
  filter(Year == 2019) %>%
ggplot(aes(x = Happiness, y = Freedom)) +
  geom_point(color = "plum4") + 
  facet_wrap(.~Region) +
labs( title = "How are freedom and happiness related",
  x = "Happiness") 
```

## 

```{r}
happydata %>% 
  filter(Year == 2019) %>%
ggplot(aes(x = Happiness, y = Generosity)) +
  geom_point(color = "plum4") + 
  facet_wrap(.~Region) +
labs( title = "How are happiness and generosity related?",
      x = "Happiness") 
```
